Throughput Prediction on 60 GHz Devices for Latency Sensitive Applications

### 2021-01-21 paper.tex
changes

We collected a total of XX hours of traces consisting of XX samples.

@@

\textbf{RNN20}: same as BP8, but takes information in the past 20 windows as input.
\Comment{Do we need to explain why BP8 takes historic values of only throughput, but RNN takes historic values of all features?}

@@

\subsection{Metrics}
We evaluate the performance of the throughput prediction model in terms of 3 metrics:

>>>>

We collected a total of ?? hours of traces consisting of ?? samples.

@@

\textbf{RNN20}: same as BP8, but takes information in the past 20 windows as input.
\comment{all three types of information??}
\Comment{Do we need to explain why BP8 takes historic values of only throughput, but RNN takes historic values of all features? yes we should}

@@

\subsection{Metrics}
We evaluate the performance of each throughput prediction model in terms of 3 metrics:
